---
title: "BioMADE Experiment: Definition Complexity and Issue"
format: 
  html:
        toc: true
        number-sections: true
  pdf:
        documentclass: article
        toc: false
        number-sections: true
        keep-tex: true
        include-in-header:
                text: |
                  \usepackage{fvextra}
                  \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,commandchars=\\\{\}}
        include-before-body: 
                text: |
                  \RecustomVerbatimEnvironment{verbatim}{Verbatim}{
                  showspaces = false,
                  showtabs = false,
                  breaksymbolleft={},
                  breaklines
                  }
execute: 
  echo: false
  output: false
  warning: false
editor_options: 
  chunk_output_type: console
---

```{r}
#| label: setup
#| echo: false

source(here::here("scripts", "00_setup.R"))
source(here::here("scripts", "01_exp-cond.R"))

```

Data were collected by Qualtrics between August 29 and September 13, 2025. Of the final sample of 1,754, Qualtrics designated 1,190 responses as "good completes."

The table below shows demographic information by experimental condition--none of the differences in the demographics between conditions are significant, which is indicative of random assignment to the experimental conditions.

```{r}
#| label: demographics
#| echo: false
#| output: true

clean |>
    tbl_summary(by = stim,
    include = c(age, female, white, educ, income),
    label = list(
      age = "Age",
      female = "Gender",
      white = "Race (Non-White/White)",
      educ = "Education",
      income = "Income"  
    ),
    missing = c("no"),
    statistic = list(
                    all_continuous() ~ "{mean} ({sd})",
                    all_categorical() ~ "{p}%"
                )) |>
    add_p(pvalue_fun = label_style_pvalue(digits = 2)) |>
    add_overall() |>
    modify_caption("Demographic characteristics of respondents by experimental condition.")

```

# Manipulation Checks

The first manipulation check is a question about the perceived difficulty of understanding the definition provided in the survey.

```{r}
#| label: defn-manip-check
#| echo: false
#| output: true
#| fig-cap: Mean levels of perceived difficulty of understanding the definition provided in the survey by simple vs. complex definition.
#| fig-width: 5in
#| fig-height: 5in

clean |>
    ggplot(aes(x = defn, y = MCself)) +
    scale_y_continuous(name = "Perceived difficulty of definition",
                           limits = c(1,7), # y-axis scale
                           breaks = seq(1, 7, 1),
                           expand = c(0,0)) +
    scale_x_discrete(name = "", labels = c("simple definition",
                                                            "complex definition")) +
    theme_bw() +
    stat_summary(fun = mean, geom = "point") +
    stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = 0.2)

```