---
title: "BioMADE Experiment: Definition Complexity and Issue"
format: 
  html:
        toc: true
        number-sections: true
  pdf:
        documentclass: article
        toc: false
        number-sections: true
        keep-tex: true
        include-in-header:
                text: |
                  \usepackage{fvextra}
                  \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,commandchars=\\\{\}}
        include-before-body: 
                text: |
                  \RecustomVerbatimEnvironment{verbatim}{Verbatim}{
                  showspaces = false,
                  showtabs = false,
                  breaksymbolleft={},
                  breaklines
                  }
execute: 
  echo: false
  output: false
  warning: false
editor_options: 
  chunk_output_type: console
---

```{r}
#| label: setup
#| echo: false

source(here::here("scripts", "00_setup.R"))
source(here::here("scripts", "01_exp-cond.R"))

```

Data were collected by Qualtrics between August 29 and September 13, 2025. Of the final sample of 1,754, Qualtrics designated 1,190 responses as "good completes."

The table below shows demographic information by experimental condition--none of the differences in the demographics between conditions are significant, which is indicative of random assignment to the experimental conditions.

```{r}
#| label: demographics
#| echo: false
#| output: true

clean |>
  tbl_summary(
    # by = stim,
    include = c(age, female, white, educ, income),
    label = list(
      age = "Age",
      female = "Gender",
      white = "Race (Non-White/White)",
      educ = "Education",
      income = "Income"
    ),
    missing = c("no"),
    statistic = list(
      all_continuous() ~ "{mean} ({sd})",
      all_categorical() ~ "{p}%"
    )
  ) |>
 modify_caption("Demographic characteristics of respondents by experimental condition.")

```

# Manipulation Checks
## Perceived difficulty of self-understanding provided definition

The first manipulation check is a question about the perceived difficulty (be the respondent) of understanding the definition provided in the survey. The figure below shows mean levels of perceived difficulty of understanding the definition provided in the survey by simple vs. complex definition. The difference in mean levels of perceived difficulty was significant between the conditions ($t = -2.67$, $p = .008$).

```{r}
#| label: defn-MC-self
#| echo: false
#| output: true
#| fig-align: center

clean |>
  ggplot(aes(x = defn, y = MCself)) +
  scale_y_continuous(
    name = "Perceived difficulty of definition (self)",
    limits = c(1, 7), # y-axis scale
    breaks = seq(1, 7, 1),
    expand = c(0, 0)
  ) +
  scale_x_discrete(name = "", labels = c(
    "simple definition",
    "complex definition"
  )) +
  theme_bw() +
  stat_summary(fun = mean, geom = "point") +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = 0.2)

```

## Perceived difficulty of other-understanding provided definition

The second manipulation check question asked respondents about their perceptions of how difficult it might be for others to understand the provided definition. The figure below shows mean levels of perceived difficulty that others might have understanding the definitions provided in the survey. The difference in mean levels of perceived difficulty was significant between the conditions ($t = -3.13$, $p = .002$).

```{r}
#| label: defn-MC-other
#| echo: false
#| output: true
#| fig-align: center

clean |>
  ggplot(aes(x = defn, y = MCother)) +
  scale_y_continuous(
    name = "Perceived difficulty of definition (others)",
    limits = c(1, 7), # y-axis scale
    breaks = seq(1, 7, 1),
    expand = c(0, 0)
  ) +
  scale_x_discrete(name = "", labels = c(
    "simple definition",
    "complex definition"
  )) +
  theme_bw() +
  stat_summary(fun = mean, geom = "point") +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = 0.2)

```

I was not sure what to do with the question about the terms used in the definition or the open-ended questions, which require coding.

# Dependent Variables

```{r}
#| label: DVs
#| echo: false
#| output: false

source(here::here("scripts", "02_DVs.R"))

```

## Curiosity

Created a variable from the items measuring curiosity in each of the experimental conditions (`Q29_1`: `Q29_4`, `Q44_1`:`Q44_4`, `Q59_1`:`Q59_4`, `Q74_1`:`Q74_4`). The table below shows the means and standard deviations for this variable in the whole sample, as well as in the four experimental conditions. Analysis of variance (ANOVA) reveals no significant differences in the mean of curiosity between the conditions ($F(3, 1185) = 0.34$, $p = .80$).

```{r}
#| label: curious
#| echo: false
#| output: true
#| fig-align: center

# clean |>
#   tbl_summary(
#     by = stim,
#     include = c(curious),
#     label = list(
#       curious = "Curiosity"
#     ),
#     missing = c("no"),
#     statistic = list(
#       all_continuous() ~ "{mean} ({sd})"
#     )
#   ) |>
#   add_p(
#     test = everything() ~ "oneway.test",
#     pvalue_fun = label_style_pvalue(digits = 2)
#   ) |>
#   add_overall() |>
#   modify_caption(
#     "Descriptive statistics of the variable measuring curiosity post-exposure to the stimulus."
#   )

clean |>
  ggplot(aes(x = stim, y = curious)) +
  scale_y_continuous(
    name = "Curiosity",
    limits = c(1, 7), # y-axis scale
    breaks = seq(1, 7, 1),
    expand = c(0, 0)) +
  scale_x_discrete(
    name = "",
    labels = c(
      "simple/fabrics",
      "complexfabrics",
      "simple/makeup",
      "complex/makeup"
    )) +
  theme_bw() +
  stat_summary(fun = mean, geom = "point") +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = 0.2)


```


## Information Seeking

Created a variable from the items measuring intentions to seek information in each of the experimental conditions (`Q30_1`: `Q30_5`, `Q45_1`:`Q45_5`, `Q60_1`:`Q60_5`, `Q75_1`:`Q75_5`). The table below shows the means and standard deviations for this variable in the whole sample, as well as in the four experimental conditions. There were no significant differences in this outcome variable by experimental condition ($F(3, 1186) = .51$, $p = .68$).

```{r}
#| label: infoseek
#| echo: false
#| output: true
#| fig-align: center

# clean |>
#   tbl_summary(
#     by = stim,
#     include = c(infoseek),
#     label = list(
#       infoseek = "Likelihood of seeking information"
#     ),
#     missing = c("no"),
#     statistic = list(
#       all_continuous() ~ "{mean} ({sd})")) |>
#   add_p(test = everything() ~ "oneway.test",
#         pvalue_fun = label_style_pvalue(digits = 2)) |>
#   add_overall() |>
#   modify_caption(
#     "Descriptive statistics of the variable measuring information-seeking intentions post-exposure to the stimulus."
#   )

  clean |>
  ggplot(aes(x = stim, y = infoseek)) +
  scale_y_continuous(
    name = "Intentions to seek information",
    limits = c(1, 7), # y-axis scale
    breaks = seq(1, 7, 1),
    expand = c(0, 0)) +
  scale_x_discrete(
    name = "",
    labels = c(
      "simple/fabrics",
      "complexfabrics",
      "simple/makeup",
      "complex/makeup"
    )) +
  theme_bw() +
  stat_summary(fun = mean, geom = "point") +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = 0.2)

```

## Support for Biomanufacturing, Federal and State Funding of Research 

Created a variable from the items measuring intentions to seek information in each of the experimental conditions (`Q31_1`: `Q31_3`, `Q46_1`:`Q46_3`, `Q61_1`:`Q61_3`, `Q76_1`:`Q76_3`). The table below shows the means and standard deviations for this variable in the whole sample, as well as in the four experimental conditions. There were no significant differences in the means of support by experimental condition ($F(3, 1186) = .75$, $p = .53$). 

Even though the factor analysis revealed a single factor for this variable, it might be worth considering (for content validity) separating general support for biomanufacturing and support for funding (state and federal) of biomanufacturing research.

```{r}
#| label: support
#| echo: false
#| output: true
#| fig-align: center

# clean |>
#   tbl_summary(
#     by = stim,
#     include = c(support),
#     label = list(
#       support = "Support for biomanufacturing"
#     ),
#     missing = c("no"),
#     statistic = list(
#       all_continuous() ~ "{mean} ({sd})")) |>
#   add_p(test = everything() ~ "oneway.test",
#         pvalue_fun = label_style_pvalue(digits = 2)) |>
#   add_overall() |>
#   modify_caption(
#     "Descriptive statistics of the variable measuring support for biomanufacturing and state and federal funding of biomanufacturing research post-exposure to the stimulus."
#   )

  clean |>
  ggplot(aes(x = stim, y = support)) +
  scale_y_continuous(
    name = "Support for biomanufacturing",
    limits = c(1, 7), # y-axis scale
    breaks = seq(1, 7, 1),
    expand = c(0, 0)) +
  scale_x_discrete(
    name = "",
    labels = c(
      "simple/fabrics",
      "complexfabrics",
      "simple/makeup",
      "complex/makeup"
    )) +
  theme_bw() +
  stat_summary(fun = mean, geom = "point") +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = 0.2)

```


## Risks and Benefits

Created a variable from the single items each measuring risk and benefit perceptions in each of the experimental conditions (`Q31_4`, `Q31_5`, `Q46_4`, `Q46_5`, `Q61_4`, `Q61_5`, `Q76_4`, `Q76_5`). The table below shows the means and standard deviations for this variable in the whole sample, as well as in the four experimental conditions. There were no significant differences in perceived benefits between conditions ($F(3, 1183) = .19$, $p = .90$). However, there were significant differences in risk perceptions by experimental conditions ($F(3,1186) = 3.27$, $p = .02$).

```{r}
#| label: risks
#| echo: false
#| output: true
#| fig-align: center

# clean |>
#   tbl_summary(
#     by = stim,
#     include = c(risks),
#     label = list(
#       curious = "Perceived risks of biomanufacturing"
#     ),
#     missing = c("no"),
#     statistic = list(
#       all_continuous() ~ "{mean} ({sd})")) |>
#   add_p(test = everything() ~ "oneway.test",
#         pvalue_fun = label_style_pvalue(digits = 2)) |>
#   add_overall() |>
#   modify_caption(
#     "Descriptive statistics of the variable measuring perceived risks of biomanufacturing post-exposure to the stimulus."
#   )

  clean |>
  ggplot(aes(x = stim, y = risks)) +
  scale_y_continuous(
    name = "Perceived risks of biomanufacturing",
    limits = c(1, 7), # y-axis scale
    breaks = seq(1, 7, 1),
    expand = c(0, 0)) +
  scale_x_discrete(
    name = "",
    labels = c(
      "simple/fabrics",
      "complexfabrics",
      "simple/makeup",
      "complex/makeup"
    )) +
  theme_bw() +
  stat_summary(fun = mean, geom = "point") +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = 0.2)

```

```{r}
#| label: benefits
#| echo: false
#| output: true
#| fig-align: center

# clean |>
#   tbl_summary(
#     by = stim,
#     include = c(benefits),
#     label = list(
#       benefits = "Perceived benefits of biomanufacturing"
#     ),
#     missing = c("no"),
#     statistic = list(
#       all_continuous() ~ "{mean} ({sd})")) |>
#   add_p(test = everything() ~ "oneway.test",
#         pvalue_fun = label_style_pvalue(digits = 2)) |>
#   add_overall() |>
#   modify_caption(
#     "Descriptive statistics of the variable measuring perceived benefits of biomanufacturing post-exposure to the stimulus."
#   )

  clean |>
  ggplot(aes(x = stim, y = benefits)) +
  scale_y_continuous(
    name = "Perceived benefits of biomanufacturing",
    limits = c(1, 7), # y-axis scale
    breaks = seq(1, 7, 1),
    expand = c(0, 0)) +
  scale_x_discrete(
    name = "",
    labels = c(
      "simple/fabrics",
      "complexfabrics",
      "simple/makeup",
      "complex/makeup"
    )) +
  theme_bw() +
  stat_summary(fun = mean, geom = "point") +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = 0.2)

```