---
title: "BioMADE Experiment: Definition Complexity and Issue"
format: 
  html:
        toc: true
        number-sections: true
  pdf:
        documentclass: article
        toc: false
        number-sections: true
        keep-tex: true
        include-in-header:
                text: |
                  \usepackage{fvextra}
                  \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,commandchars=\\\{\}}
        include-before-body: 
                text: |
                  \RecustomVerbatimEnvironment{verbatim}{Verbatim}{
                  showspaces = false,
                  showtabs = false,
                  breaksymbolleft={},
                  breaklines
                  }
execute: 
  echo: false
  output: false
  warning: false
editor_options: 
  chunk_output_type: console
---

```{r}
#| label: setup
#| echo: false

source(here::here("scripts", "00_setup.R"))
source(here::here("scripts", "01_exp-cond.R"))

```

Data were collected by Qualtrics between August 29 and September 13, 2025. Of the final sample of 1,754, Qualtrics designated 1,190 responses as "good completes."

The table below shows demographic information by experimental condition--none of the differences in the demographics between conditions are significant, which is indicative of random assignment to the experimental conditions.

```{r}
#| label: demographics
#| echo: false
#| output: true

clean |>
    tbl_summary(
        by = stim,
        include = c(age, female, white, educ, income),
        label = list(
            age = "Age",
            female = "Gender",
            white = "Race (Non-White/White)",
            educ = "Education",
            income = "Income"
        ),
        missing = c("no"),
        statistic = list(
            all_continuous() ~ "{mean} ({sd})",
            all_categorical() ~ "{p}%"
        )
    ) |>
    add_p(pvalue_fun = label_style_pvalue(digits = 2)) |>
    add_overall() |>
    modify_caption("Demographic characteristics of respondents by experimental condition.")

```

# Manipulation Checks
## Perceived difficulty of self-understanding provided definition

The first manipulation check is a question about the perceived difficulty (be the respondent) of understanding the definition provided in the survey. The figure below shows mean levels of perceived difficulty of understanding the definition provided in the survey by simple vs. complex definition. The difference in mean levels of perceived difficulty was significant between the conditions ($t = -2.67$, $p = .008$).

```{r}
#| label: defn-MC-self
#| echo: false
#| output: true
#| fig-align: center
#| fig-width: 5
#| fig-height: 5

clean |>
    ggplot(aes(x = defn, y = MCself)) +
    scale_y_continuous(
        name = "Perceived difficulty of definition (self)",
        limits = c(1, 7), # y-axis scale
        breaks = seq(1, 7, 1),
        expand = c(0, 0)
    ) +
    scale_x_discrete(name = "", labels = c(
        "simple definition",
        "complex definition"
    )) +
    theme_bw() +
    stat_summary(fun = mean, geom = "point") +
    stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = 0.2)

```

## Perceived difficulty of other-understanding provided definition

The second manipulation check question asked respondents about their perceptions of how difficult it might be for others to understand the provided definition. The figure below shows mean levels of perceived difficulty that others might have understanding the definitions provided in the survey. The difference in mean levels of perceived difficulty was significant between the conditions ($t = -3.13$, $p = .002$).

```{r}
#| label: defn-MC-other
#| echo: false
#| output: true
#| fig-align: center
#| fig-width: 5
#| fig-height: 5

clean |>
    ggplot(aes(x = defn, y = MCother)) +
    scale_y_continuous(
        name = "Perceived difficulty of definition (others)",
        limits = c(1, 7), # y-axis scale
        breaks = seq(1, 7, 1),
        expand = c(0, 0)
    ) +
    scale_x_discrete(name = "", labels = c(
        "simple definition",
        "complex definition"
    )) +
    theme_bw() +
    stat_summary(fun = mean, geom = "point") +
    stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = 0.2)

```

I was not sure what to do with the question about the terms used in the definition or the open-ended questions, which require coding.

# Dependent Variables

```{r}
#| label: DVs
#| echo: false
#| output: false

source(here::here("scripts", "02_DVs.R"))

```

## Curiosity

Created a variable from the items measuring curiosity in each of the experimental conditions (`Q29_1`: `Q29_4`, `Q44_1`:`Q44_4`, `Q59_1`:`Q59_4`, `Q74_1`:`Q74_4`). 

```{r}
#| label: curious
#| echo: false
#| output: true

clean |>
    tbl_summary(
        by = stim,
        include = c(curious),
        label = list(
            curious = "Curiosity"
        ),
        missing = c("no"),
        statistic = list(
            all_continuous() ~ "{mean} ({sd})"
        )
    ) |>
    add_overall() |>
    modify_caption("Descriptive statistics of the variable measuring curiosity post-exposure to the stimulus.")

```